Measurement of CO2 from carbonate minerals using a hybrid sputter gas ion source with an open split interface

### 2021-08-17 doc/AMS-15/AMS15_abstract.Rmd
update abstract

---
title: "Measurement of CO2 from carbonate minerals using a hybrid sputter gas ion source with an open split interface"
author:
- Brett Longworth
- Josh Burton
- Simon Pendleton
- Josh Hlavenka
- Mark Roberts
output:
  pdf_document: default
  html_document: default
  word_document: default
---

@@

We have developed a method for radiocarbon measurement of carbonate minerals as CO~2~ gas via a hybrid sputter gas ion source. Our method uses a carrier gas to displace CO~2~ from sample vials to an open split, where a capillary samples the mixture for delivery directly to a hybrid sputter gas ion source (HGIS). This method skips the gas transfer and quantification steps used in a closed inlet HGIS system, simplifying sample measurement. Results from measurements of consensus standards and samples from a marine core show that the method agrees well with traditional AMS measurement of the same samples, and that the method error is less than 1.5%. We discuss advantanges and disadvantanges of continuous flow sample introduction.

>>>>

---
title: "Measurement of CO2 from carbonate minerals using a hybrid sputter gas ion source with an open split interface"
author:
- Brett Longworth
- Josh Burton
- Simon Pendleton
- Josh Hlavenka
- Sydney Moser
- Mark Roberts
output:
  word_document: default
  html_document: default
  pdf_document: default
---

@@

We have developed a method for measurement of radiocarbon in carbonate minerals
as CO~2~ gas via a NEC MCSNICS hybrid sputter gas ion source. Our method uses a
carrier gas to displace CO~2~ from sample vials to an open split, where a
capillary samples the mixture for delivery directly to a hybrid sputter gas ion
source (HGIS).  This method skips the gas transfer and quantification steps
used in a closed inlet HGIS system, simplifying sample measurement. Results
from measurements of consensus standards (TIRI-I, IAEA C2, and an internal
modern shell standard), and samples from a marine core show that the method
agrees well with traditional AMS measurement of the same samples, and that the
method error is less than 1.5%. We discuss advantanges and disadvantanges of
continuous flow sample introduction.
